Efficient and Robust Boolean Operations on N Meshes Based on Hybrid Representations

### 2017-01-19 tex/exp.tex
谁来抄这篇论文？

\vspace{0.5em}
\noindent\textbf{Searching valid loops}~~~~ %In \S\ref{sec:tess}, we claim a valid loops on tess-graph has to be correct with its orientation. However, since tess-graph is undirectional, it is not easy to check whether a loop orientation agrees with the face's (Fig. \ref{fig:dual}a). We observe that the graph connections on the triangle edges have unambiguous directions. Starting from these edges, we can guarantee that the loops have the right orientations. After we find a valid loop, more graph connections will have unambiguous directions because one connection can participate at most two valid loops. In such way, the correct orientation will propagate in a flood-filling way.
Searching valid loops In \S\ref{sec:tess}, we stated that a valid loop on a tess-graph must correspond to its orientation. However, as a tess-graph is nondirectional, it is difficult to check whether a loop orientation agrees with that of the face (Fig. \ref{fig:dual}a). The graph connections on the triangle edges have unambiguous directions. Thus, starting from these edges, we can guarantee that the loops will have the right orientations. After a valid loop is found, more graph connections will have unambiguous directions, because one connection can participate in two valid loops at most. Therefore, the correct orientation will propagate in a flood-filling manner.

\vspace{0.5em}% There is another problem that the tess-graph may not be a connected graph. We avoid this problem by inserting auxiliary intersections into the tess-graph to make it connected. An auxiliary intersection links the corner vertex of triangle face (denoted as $\bm{v}_i$), which is certainly on the outer component, with the vertex on the inner component. The intersection refinement has to be performed again if the auxiliary intersections cross any other intersections. This trick slight obey the principle of no constructions. To guarantee the auxiliary intersection has a valid PBI-rep, we require the vertex from inner connected component generated by intersection between the triangle and an edge (denoted as $\bm{e}_j$) from other meshes---all intersection end points during triangle-triangle intersection are this type. In this way, we get three vertices with exact coordinates ($\bm{v}_i$ and the two end points of $\bm{e}_j$) and can construct an exact plane where the auxiliary intersection lies.
There is no guarantee that the tess-graph will be a connected graph. We solve this problem by inserting auxiliary intersections into the tess-graph, to ensure it is connected. An auxiliary intersection links the corner vertex ( $\bm{v}_i$) of a triangle face which is confirmed to be on the outer component, with the vertex on the inner component. The intersection refinement needs to be performed again if the auxiliary intersections cross any other intersections. This solution is consistent with the principle of no constructions. To guarantee that the auxiliary intersection has a valid PBI-rep, the vertex must be determined from the inner connected component generated by the intersection between the triangle and an edge (denoted as $\bm{e}_j$) from another mesh. All intersection end points of triangle-triangle intersections are of this type. Therefore, we obtain three vertices with exact coordinates ($\bm{v}_i$ and the two end points of $\bm{e}_j$), and, therefore, can construct the plane on which the auxiliary intersection lies.

>>>>

\vspace{0.5em}
\noindent\textbf{Tess-graph with multiple components}~~~~
% There is another problem that the tess-graph may not be a connected graph. We avoid this problem by inserting auxiliary intersections into the tess-graph to make it connected. An auxiliary intersection links the corner vertex of triangle face (denoted as $\bm{v}_i$), which is certainly on the outer component, with the vertex on the inner component. The intersection refinement has to be performed again if the auxiliary intersections cross any other intersections. This trick slight obey the principle of no constructions. To guarantee the auxiliary intersection has a valid PBI-rep, we require the vertex from inner connected component generated by intersection between the triangle and an edge (denoted as $\bm{e}_j$) from other meshes---all intersection end points during triangle-triangle intersection are this type. In this way, we get three vertices with exact coordinates ($\bm{v}_i$ and the two end points of $\bm{e}_j$) and can construct an exact plane where the auxiliary intersection lies.
There is no guarantee that the tess-graph will be a connected graph. We solve this problem by inserting auxiliary intersections into the tess-graph, to ensure it is connected. An auxiliary intersection links the corner vertex ( $\bm{v}_i$) of a triangle face which is confirmed to be on the outer component, with the vertex on the inner component. The intersection refinement needs to be performed again if the auxiliary intersections cross any other intersections. This solution is consistent with the principle of no constructions. To guarantee that the auxiliary intersection has a valid PBI-rep, the vertex must be determined from the inner connected component generated by the intersection between the triangle and an edge (denoted as $\bm{e}_j$) from another mesh. All intersection end points of triangle-triangle intersections are of this type. Therefore, we obtain three vertices with exact coordinates ($\bm{v}_i$ and the two end points of $\bm{e}_j$), and, therefore, can construct the plane on which the auxiliary intersection lies.

### 2017-01-19 tex/intro.tex
谁来抄这篇论文？

\IEEEtitleabstractindextext{
\begin{abstract}
  Constructive solid geometry (CSG) is widely used in computer aided design and manufacturing. However, boolean algorithms, which compute the boundary representations of CSG, have suffered from robustness and efficiency problems for more than three decades. We propose a fast and robust boolean operation method which is unconditionally robust for valid solids. Previously reported boolean methods using plane-based representations (P-reps) of polyhedrons are robust, but inefficient. Conversely, methods based on vertex-based representations (V-reps) are fast but not robust, unless exact arithmetic is applied. We choose to combine P-reps with V-reps, which allowed us to use the advantages of both. Our method uses V-reps for efficiency and uses P-reps to ensure robustness. Comparison experiments with the state-of-the-art show that our method is unconditionally robust, and similarly efficient to existing non-robust methods.
\end{abstract}

@@

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{C}{onstructive} solid geometry (CSG) has long been a popular modeling tool for computer-aided design and computer-aided manufacturing (CAD / CAM). Complex models are constructed by combining primitives using regularized boolean operations \cite{requicha1977mathematical,tilove1980closure}: union, intersection, and difference. A CSG can be converted into the boundary representation (B-rep) through boolean algorithms. There are two major types of boolean algorithms, which vary according to how they deal with intersections between primitives. Approximate methods \cite{wang2011approximate,pavic2010hybrid,biermann2001approximate} rediscretize the intersection areas, fit vertices approximatively, and rearrange the topology. Conversely, exact methods \cite{ogayar2015deferred,douze2015quickcsg,zhou2016mesh} do not change vertex positions, and maintain as many input elements (such as faces, vertices, and topology) as possible. In many applications, exact methods are preferred for their accuracy. Additionally, the clear mapping between the surfaces of the input and output meshes in exact methods simplifies the inheritance of surface information, such as face colors and materials.

However, there is always a compromise between robustness and efficiency for exact boolean algorithms.
Robust methods often require exact arithmetics \cite{barki2015exact,zhou2016mesh}, which is significantly slower than normal floating point arithmetic.
Other methods only offer \textbf{quasi-robust} \cite{shewchuk1999lecture} implementations by using unreliable techniques, such as epsilon-tweaking \cite{laidlaw1986constructive,feito2013fast,segal1990using} and numerical pertubation on coordinates \cite{douze2015quickcsg}.
Recently, robust methods have been developed \cite{bernstein2009fast,campen2010exact} based on binary space partition (BSP) merging routines \cite{naylor1990merging,thibault1987set}.
The robustness of these methods are guaranteed by the theorem of Sugihara and Iri \cite{sugihara1990solid} that boolean operations can be performed without \textbf{constructions} \cite{shewchuk1999lecture} if polyhedrons are represented based on planes instead of vertices.
By only use \textbf{predicates}, implementations of boolean operations are easier to be robust.
These BSP-based methods are generally faster than other boolean algorithms using exact arithmetics. However, they still suffer from performance issues because of the complex conversions between vertex-based representations (V-reps) and plane-based representations (P-reps). In addition, the incoherence between V-reps and P-reps requires that extra steps to reconstruct connectivity, leading to complex implementations and worse performance.

Inspired by these previous studies, we have developed a robust boolean operation method, which is unconditionally robust given consistent input, and as fast as non-robust methods. In our method, we combine P-reps with V-reps, forming hybrid representations of meshes. To ensure robustness, we avoid constructions throughout our method, and only performing exact predicates. Numerical filters \cite{shewchuk1997adaptive} are applied to guarantee performance. Generally, the V-reps information is used for coarse tests and efficient neighboring face queries, while P-reps information is used for exact predicates.

Our method is different from the previous BSP-based methods \cite{bernstein2009fast,campen2010exact}.
While their methods are largely based on BSP theorem of \cite{naylor1990merging,thibault1987set}, our method is more like V-reps methods such as \cite{feito2013fast,zhou2016mesh} and is significantly faster. Our method is not a simple improvement of V-reps methods, but an efficient and systematical solution for robustness of boolean operations. During intersection computation, we encode the triangle intersections into sets of planes, and then use these planes to determine exact tessellations. Subsequently, we classify each face in the tessellated meshes using local binary space partition (BSP) trees, which also compliment the P-reps to guarantee exactness. In addition, while most existing boolean operations can only process two meshes, our method is varadic \cite{zhou2016mesh}, which can evaluate arbitrary inputs immediately. Thus, our method may reduces computation time in large cases by avoiding repetitive operations. Experiments have shown that our method is much faster than existing robust methods, and only around two times slower than non-robust exact methods.

%Because computations based on P-reps are slower, we develop a set of algorithms

@@

Boolean operations have been researched since their inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}. Existing methods can be put into two categories: exact methods and approximate methods. Exact methods retain vertex positions, and the topology of the inputs is preserved as much as possible. The coordinates of intersection points between input meshes are computed by input configurations. However, the coordinates cannot be represented exactly using fixed-precision floating point numbers, hence robustness is a significant problem. Conversely, approximate methods rediscretize the input mesh surfaces using techniques such as voxels, octrees, and Layered Depth Images (LDI). These methods generally have better performance and robustness than exact methods, but the loss of precision and geometry information is inevitable. In this section, we first introduce previous work of these two categories, and then discuss plane-based boolean algorithms, which have close relation with our method.

@@

Some exact methods \cite{ogayar2015deferred,douze2015quickcsg,zhou2016mesh,xu2013fast,feito2013fast}, are optimized for efficiency, but cannot guarantee robustness. They are implemented by fixed-precision floating point arithmetic, so numerical errors are inevitable, which often leads to incorrect results.
Douze et al. \cite{douze2015quickcsg} developed a very efficient method for handling very large meshes. In addition, their method is varadic, which means it can perform boolean operations with arbitrary number of inputs. However, this method makes general position assumption and cannot deal with coplanar situations. However, large CSGs are more complex, and thus more likely to contain degenerate cases, and more vulnerable to numerical errors.

Many researchers have attempted to solve the robustness issues using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}. However, these methods are too expensive in terms of computation time and memory. For example, CGAL's \cite{cgal:hk-bonp3-15a} exact-arithmetic implementation \cite{granados2003boolean} of Nef polyhedra \cite{bieri1988elementary} is more than 50 times slower than non-robust boolean operations \cite{bernstein2009fast}.

@@

Because it is difficult to achieve efficiency, accuracy, and robustness simultaneously, some methods sacrifice accuracy for greater efficiency and robustness. Most such methods are based on volumetric representations of meshes. However, the quality of the resulting mesh depends on the resolution of the volume grid, and better quality require significantly higher resolutions.
To accelerate this process, some methods reduce the complexity of the output mesh \cite{varadhan2004topology}, whereas others preserve non-intersected areas of the input mesh to avoid redundant tessellation \cite{pavic2010hybrid,wang2011approximate,zhao2011parallel,hable2005blister,ogayar2006gpu}.
Moreover, with the development of general-purpose computing on graphics processing units (GPGPU), many of them utilize the computational power of graphics hardware for boolean operations. These methods have good performance, and are suitable for interactive applications. However, the fundamental problem of approximate methods arises from the grid-dependent nature of volumetric calculations; they inevitably suffer from geometric detail loss and unwieldy topological changes.

@@

The concept of plane-based representations (P-reps) of polyhedrons was first described by Sugihara and Iri \cite{sugihara1990solid}. By using P-reps, boolean operations can be performed with only predicates, which are much easier to implement accurately and robustly. Berstein and Fussell \cite{bernstein2009fast} combined P-reps with binary space partition (BSP) trees \cite{thibault1987set,naylor1990merging} to develop a boolean operation method which is unconditionally robust with consistent inputs. Unlike methods based on vertex-based representations, this method does not rely on exact arithmetic to be robust.
However, the merging of two BSP trees is has $O(mn)$ time complexity, where $m$ and $n$ are the size of the trees. This time complexity makes this method impractical for large meshes. Subsequently, Campen and Kobbelt \cite{campen2010exact} improved this method by localizing BSP operations using an octree. In this method, mesh refinements only take place locally, near intersections, which leads to better performance. However, their method splits the intersection regions and non-intersection regions, and requires extra stitching step to reconstruct topology. Also, the performance of localized BSP merging is still poor compared with vertex-based boolean methods.

>>>>

\IEEEtitleabstractindextext{
\begin{abstract}
  Constructive solid geometry (CSG) is a widely used modeling tool. It constructs complex models by combining primitive solids with boolean operations. However, boolean evaluation, which computes the final model of CSG, has suffered from robustness problem for more than three decades. Some methods are fast but not robust, while some methods are robust but rely on exact arithmetic which is slow. Recent works tried to implement fast and robust boolean evaluation methods using plane-based representations (P-reps) of polyhedrons instead of vertex-based representations (V-reps) of polyhedrons. While they have achieved remarkable improvements, they are still slow compared with non-robust methods. We propose a fast and robust boolean method. It uses hybrid representations of polyhedrons, which combines P-reps with V-reps. It allows us to take advantages of both the efficiency of V-reps and the exactness of P-reps. Comparison experiments with the state-of-the-art show that our method is unconditionally robust for solid inputs, and is similarly efficient to existing non-robust methods.
\end{abstract}

@@

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{C}{onstructive} solid geometry (CSG) has long been a popular modeling tool for computer-aided design and computer-aided manufacturing (CAD / CAM). Complex models are constructed by combining primitives using regularized boolean operations \cite{requicha1977mathematical,tilove1980closure}: union, intersection, and difference. A CSG can be converted into the boundary representation (B-rep) through boolean evaluation. There are two major types of boolean evaluation methods, which vary according to how they deal with intersections between primitives.
Approximate methods \cite{wang2011approximate,pavic2010hybrid,biermann2001approximate} rediscretize the intersection areas, fit vertices approximatively, and rearrange the topology.
Conversely, exact methods \cite{ogayar2015deferred,douze2015quickcsg,zhou2016mesh} do not change vertex positions, and maintain as many input elements (such as faces, vertices, and topology) as possible. In many applications, exact methods are preferred for their accuracy. Additionally, the clear mapping between the surfaces of the input and output meshes in exact methods simplifies the inheritance of surface information, such as face colors and materials.

However, there is always a compromise between robustness and efficiency for exact boolean algorithms.
Robust methods often require exact arithmetic \cite{barki2015exact,zhou2016mesh}, which is significantly slower than normal floating-point arithmetic.
Other methods only guarantee \textbf{quasi-robust} \cite{shewchuk1999lecture} by using unreliable techniques, such as epsilon-tweaking \cite{laidlaw1986constructive,feito2013fast,segal1990using} and numerical perturbation \cite{douze2015quickcsg}.
Recently, robust plane-based methods have been developed \cite{bernstein2009fast,campen2010exact} based on binary space partition (BSP) merging algorithms \cite{naylor1990merging,thibault1987set}.
The robustness of these methods is guaranteed by the theorem of Sugihara and Iri \cite{sugihara1990solid} that boolean evaluations can be performed without \textbf{constructions} \cite{shewchuk1999lecture} if polyhedrons are represented based on planes instead of vertices.
By only use \textbf{predicates}, boolean methods are easier to be robust.
These plane-based methods are generally faster than others which using exact arithmetic. However, they still suffer from performance issues because of the high computation complexity of BSP algorithms. In addition, the incoherence between BSP representations and B-reps of polyhedrons requires that extra steps for conversion and connectivity reconstruction, leading to worse performance.

Inspired by these previous studies, we develop a robust boolean method, which is unconditionally robust given consistent solid inputs, and as fast as non-robust methods. In our method, we combine P-reps with V-reps, forming hybrid representations of solids. Generally, the V-reps information is used for coarse tests and efficient neighboring face queries, while P-reps information is used for exact predicates. To avoid using exact arithmetic and ensure efficiency, we avoid constructions throughout our method.

Our method is different from the previous BSP-based methods \cite{bernstein2009fast,campen2010exact}.
While their methods are largely based on BSP theorem of \cite{naylor1990merging,thibault1987set}, our method is more like vertex-based methods such as \cite{feito2013fast,zhou2016mesh} and is significantly faster than these BSP-based methods. Our method is not a simple improvement of vertex-based methods, but a systematical solution for robustness of boolean evaluations. During intersection computation, we encode the triangle intersections into sets of planes, and then use these planes to determine exact tessellations. Subsequently, we classify each face in the tessellated meshes using small local BSP trees, which also compliment the P-reps to guarantee exactness. In order to guarantee performance, we try to minimize the usage of plane-based exact predicates in these stages. In addition, while most existing boolean methods can only process two meshes, our method is \textbf{variadic} \cite{zhou2016mesh}, which can evaluate arbitrary inputs immediately. Thus, our method may reduce evaluation time of large CSGs by avoiding repetitive computation. Experiments have shown that our method is much faster than existing robust methods, and only around two times slower than non-robust methods.

@@

Boolean methods have been researched since their inception in the 1980s \cite{requicha1985boolean, laidlaw1986constructive}. Existing methods can be put into two categories: exact methods and approximate methods. Exact methods retain vertex positions, and the topology of the inputs is preserved as much as possible. The coordinates of intersection points between input meshes are computed by input configurations. However, the coordinates cannot be represented exactly using fixed-precision floating point numbers, hence exact arithmetic is needed for robustness. Conversely, approximate methods rediscretize the input mesh surfaces using techniques such as voxels, octrees, and Layered Depth Images (LDI). These methods generally have better performance and easier to be robust than exact methods, but the loss of precision and geometry information is inevitable. In this section, we first introduce previous work of these two categories, and then discuss plane-based boolean methods, which have close relation with our method.

@@

Some exact methods \cite{ogayar2015deferred,douze2015quickcsg,xu2013fast,feito2013fast,updegrove2016boolean}, are optimized for efficiency, but cannot guarantee robustness. They are implemented by fixed-precision floating-point arithmetic, so numerical errors are inevitable, which often leads to inconsistent results.
Douze et al. \cite{douze2015quickcsg} developed a very efficient method for handling very large meshes and arbitrary input primitives. However, this method makes general position assumption and cannot deal with coplanar situations.

Many researchers have attempted to solve the robustness issues using arbitrary precision arithmetic \cite{banerjee1996topologically, fortune1995polyhedral, keyser2004esolid, granados2003boolean, hachenberger2005boolean, zhou2016mesh,barki2015exact} and exact interval computation \cite{fang1993robustness, hu1996robust, segal1990using}. However, these methods are too expensive in terms of computation time. For example, CGAL's \cite{cgal:hk-bonp3-15a} exact-arithmetic implementation \cite{granados2003boolean} of Nef polyhedra \cite{bieri1988elementary} is more than 50 times slower than non-robust boolean operations \cite{bernstein2009fast}.

@@

Because it is difficult to achieve efficiency, accuracy, and robustness simultaneously, some methods sacrifice accuracy for greater efficiency and robustness. Most such methods are based on volumetric representations of meshes. However, the quality of the resulting mesh depends on the resolution of the volume grid, and better quality requires significantly higher resolutions.
To accelerate this process, some methods reduce the complexity of the output mesh \cite{varadhan2004topology}, whereas others preserve non-intersected areas of the input mesh to avoid redundant tessellation \cite{pavic2010hybrid,wang2011approximate,zhao2011parallel,hable2005blister,ogayar2006gpu,updegrove2016boolean}.
Moreover, with the development of general-purpose computing on graphics processing units (GPGPU), many of them utilize the computational power of graphics hardware for boolean evaluations. These methods have good performance, and are suitable for interactive applications. However, the fundamental problem of approximate methods arises from the grid-dependent nature of volumetric calculations. They inevitably suffer from geometric detail loss and unwieldy topological changes.

@@

The concept of plane-based representations (P-reps) of polyhedrons was first described by Sugihara and Iri \cite{sugihara1990solid}. By using P-reps, boolean evaluations can be performed with only predicates, which are much easier to implement robustly. Berstein and Fussell \cite{bernstein2009fast} combined P-reps with BSP trees \cite{thibault1987set,naylor1990merging} to develop a boolean method which is unconditionally robust with consistent inputs. Unlike vertex-based methods, their method does not rely on exact arithmetic to be robust.
However, the merging of two BSP trees is has $O(mn)$ time complexity, where $m$ and $n$ are the size of the trees. Such high time complexity makes this method impractical for large meshes. Subsequently, Campen and Kobbelt \cite{campen2010exact} improved this method by localizing BSP operations using an octree. In this method, mesh refinements only take place locally near intersections, which leads to better performance. However, their method splits the intersection regions and non-intersection regions, and requires extra stitching step to reconstruct topology. Also, the performance of localized BSP merging is still poor compared with the vertex-based methods.
